COG-ED Manuscript

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
rearranged packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# FIXME I propose to put the packages required here at the very beginning.
library(bibtex)
```

>>>>

```{r setup, include=FALSE}

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  # we will add the package versions before submission
